PANCHANGE_analysis

### 2021-03-03 PANCHANGE_analysis.Rmd
updated forest plot styling

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian",
                             "Black",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time between lockdown and baseline")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Pre-existing mental health (Reference controls)",
                  "Gender (Reference male)",
                  "Gender (Reference male)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Age (Reference 26-35)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Ethnicity (Reference White)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Employment (Reference employed)",
                  "Other")

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by disorder no explan, fig.height=30, fig.width=50, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=50, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by time point phq, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample no explan gad, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample no explan phq, fig.height=30, fig.width=50, dpi=120}

@@

```{r forest plot by sample no explan pcl, fig.height=30, fig.width=50, dpi=120}

>>>>

  ## Row labels
  independent.variables <- c("intercept",
                             explan_var,
                             "Comorbid depression and anxiety",
                             "Depressive disorders",
                             "Anxiety disorders",
                             "Eating disorders",
                             "Obsessive compulsive disorders",
                             "Comorbid psychotic and bipolar disorders",
                             "Psychotic disorders",
                             "Bipolar disorder",
                             "Post traumatic stress disorder",
                             "Autism spectrum disorder",
                             "Attention deficit hyperactivity disorder",
                             "Personality disorders",
                             "Female",
                             "Non-binary/Self-defined",
                             "16-18",
                             "19-25",
                             "36-45",
                             "46-55",
                             "56-65",
                             "66-70",
                             "71-75",
                             "76+",
                             "Mixed or multiple ethnicities",
                             "Asian or Asian British",
                             "Black or Black British",
                             "Other",
                             "Key worker",
                             "Unemployed",
                             "Student",
                             "Retired",
                             "Time")
  ## categories to facet on  
  categories <- c("Intercept",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Pre-existing mental health",
                  "Gender",
                  "Gender",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Age",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Ethnicity",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Employment",
                  "Other")

@@

## Forest plots
### disorder
```{r forest plot by disorder prepan, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by disorder retro, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by disorder no explan, fig.height=40, fig.width=60, dpi=120}

@@

### disorder (no PCL)
```{r forest plot by disorder prepan no pcl, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by disorder retro no pcl, fig.height=40, fig.width=60, dpi=120}

@@

### time point 
```{r forest plot by time point gad, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by time point phq, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by time point pcl, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample retro only gad, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample retro only phq, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample no explan gad, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample no explan phq, fig.height=40, fig.width=60, dpi=120}

@@

```{r forest plot by sample no explan pcl, fig.height=40, fig.width=60, dpi=120}
